% !Mode:: "TeX:UTF-8"

\hitsetup{
  %******************************
  % 注意：
  %   1. 配置里面不要出现空行
  %   2. 不需要的配置信息可以删除
  %******************************
  %
  %=====
  % 秘级
  %=====
  statesecrets={公开},
  natclassifiedindex={TM301.2},
  intclassifiedindex={62-5},
  %
  %=========
  % 中文信息
  %=========
  ctitleone={生物通路网络扩展方法},%本科生封面使用
  ctitletwo={及其可视化研究},%本科生封面使用
  ctitlecover={生物通路网络扩展方法及其可视化研究},%放在封面中使用，自由断行
  ctitle={生物通路网络扩展方法及其可视化研究},%放在原创性声明中使用
  %csubtitle={一条副标题}, %一般情况没有，可以注释掉
  cxueke={工学},
  csubject={计算机科学与技术},
  caffil={计算机科学与技术学院},
  cauthor={薛晗庆},
  csupervisor={李杰副教授},
  % 日期自动使用当前时间，若需指定按如下方式修改：
  cdate={2018年06月},
  cstudentid={9527},
  cstudenttype={工程硕士}, %非全日制教育申请学位者
  %（同等学力人员）、（工程硕士）、（工商管理硕士）、
  %（高级管理人员工商管理硕士）、（公共管理硕士）、（中职教师）、（高校教师）等
  %
  %
  %=========
  % 英文信息
  %=========
  etitle={Research on biological pathway network extension and visualization method},
  esubtitle={This is the sub title},
  exueke={Engineering},
  esubject={Computer Science and Technology},
  eaffil={\emultiline[t]{School of Computer Science and Technology}},
  eauthor={Xue Hanqing},
  esupervisor={Professor Lijie},
  eassosupervisor={},
  % 日期自动生成，若需指定按如下方式修改：
  edate={June, 2018},
  estudenttype={Master of Computer Science and Technology},
  %
  % 关键词用“英文逗号”分割
  ckeywords={通路网络，网络扩展， 网络分析， 可视化 },
  ekeywords={Pathway network, Network expansion, Network Analysis, visualization techniques},
}

\begin{cabstract}

生物通路是细胞中分子间的一系列活动，导致细胞内某种产物或变化。生物通路可以导致新的分子的组装（如脂肪和蛋白质）、控制基因的表达、刺激细胞的移动等。复杂疾病往往和生物通路网络之间存在密切的关系。因此深入研究生物通路网络对探索疾病的发病机制具有重要的意义和研究价值。生物通路网络扩展算法是重要的生物通路分析方法，生物通路网络扩展算法有助于研究生物通路和复杂疾病之间的关联。然而，传统的生物网络扩展算法存在效率低和扩展效果不佳等问题。另一方面，研究者对于通路网络可视化系统具有很大需求，而现行通路可视化系统存在着授权费用高、交互体验差等问题。因此，本课题旨在提出一种高效的通路网络扩展算法，同时开发一套美观实用的生物网络可视化系统。

本课题中，我们首先使用复杂网络的分析方法分析了生物通路网络的重要参数。在网络属性方面，我们发现了生物通路网络的小世界属性和无标度性。我们研究了聚集系数、聚类系数、网络中心性、度分布等重要特性在生物通路网络中的意义。基于生物通路网络分析的结果，我们使用生物通路的聚集系数和权重提出了基于深度优先搜索策略的通路网络扩展算法。我们的算法兼顾了网络节点和边属性。我们的算法和有限随机游走算法在内的3种算法进行了比较，实验证明我们的方法兼顾了网络扩展的准确性和效率。

随着生物信息学高速发展，大量的实验数据迅速积累，由于数据规模日益增大，使用网络方法来研究这些数据已经成为了热点。随着网络可视化的需求的日益增长，因此开发一款美观实用的通路网络可视化系统迫在眉睫。本课题中，我们搭建了基于Web的生物网络可视化系统，实现生物通路网络的可视化和良好的人机交互，为使用者提供了极大便利。

\end{cabstract}

\begin{eabstract}
A biological pathway is a series of actions among molecules in a cell that leads to a certain product or a change in the cell. Such a pathway can trigger the assembly of new molecules, such as a fat or protein. Pathways can also turn genes on and off, or spur a cell to move. It is important to study relevance between complex diseases and biological pathway.Biological pathway network expansion algorithm is an important method of biological pathway analysis. Biological pathway network expansion algorithm is helpful to study the relationship between biological pathway and complex diseases.However, the traditional biological network expansion algorithm has some problems, such as low efficiency and poor expansion effect.On the other hand, the researchers have a great demand for the visualization system of biological pathway. However, the current visualization system of biological pathway has some problems, such as high authorization cost, bad user experience and so on. Therefore, the purpose of this thesis is to propose an efficient pathway network expansion algorithm, and to develop a beautiful and practical biological network visualization system at the same time.

In this paper, we first use the analysis method of complex network to analyze the important parameters of biological pathway network.We have found the small-world properties and scale-free properties of biological pathway networks.We realized the significance of aggregation coefficient, clustering coefficient, network centrality, degree distribution and other important characteristics in biological pathway networks.

Based on pathway network analysis result, we propose an extended pathway network algorithm based on depth-first search strategy using the  coefficients and weights of biological pathways. Our algorithm takes into account both the node and edge attributes of the network.Our algorithm is compared with three algorithms including limited random walk algorithm, and the experiment results show that our method takes into account the accuracy and efficiency of network expansion.

With the rapid development of bioinformatics, a large number of experimental data are accumulated rapidly.With increasing of data, network methods to study these data has become a hot topic.With the increasing demand of network visualization, it is urgent to develop a beautiful and practical visualization system of biological pathway.In this paper, we build a biological network visualization system, which provides great convenience for users.

\end{eabstract}
